Global phase diagram and possible quantum spin liquid in the triangular $J-K-\Gamma$ model

### 2020-01-02 paper/paper.tex
20200102 14:14:20

When the off-diagonal $\Gamma$ term is included, the transforamtion is no longer valid. To identify the remaining phases and providing more information of these phases, we calculate the SMSF for some representative model paramters, as shown in Fig. \ref{fig:StructureFactors}. For pure $\Gamma$ model, see Fig. \ref{fig:StructureFactors}(a) and (b), the peak of the SMSF locates at the center of first Brillouin Zone (BZ) which is a typical characteristic of the FM order. Take into account of the classical results, we propose the three blue areas with different shadings in the global phase diagram (see Fig. \ref{fig:PhaseDiagram}) to be FM ordered phases (i.e., FM-A, FM-B, FM-C) and they different from each other in the direction of the ordered moment which will be discussed in the next section.
In Fig. \ref{fig:StructureFactors}(c)-(e), the SMSF peaked at the M-points indicating that the GS of the $J-K-\Gamma$ model around these model parameters could be stripe ordered. For the model parameters shown in Fig. \ref{fig:StructureFactors}(d) and (e), the GS of the classical model is stripe ordered, and our ED results suggest the stripe state persist in the quantum limit.

@@

\textcolor{red}{$\cdots \cdots$}

\section{Moment Direction-Exact Diagonalization Results}
\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig4.pdf}
    \caption{(Color online) Map of the probabilities.}
     \label{fig:Proabilities}
\end{figure}

\textcolor{red}{Exact diagonalization results of the moment direction for FM and stripe phases. Left blank currently.}

>>>>

@@

When the off-diagonal $\Gamma$ term is included, the transforamtion is no longer valid. To identify the remaining phases and providing more information of these phases, we calculate the SMSF for some representative model paramters, as shown in Fig. \ref{fig:StructureFactors}. For pure $\Gamma$ model, see Fig. \ref{fig:StructureFactors}(a) and (b), the peak of the SMSF locates at the center of first Brillouin Zone (BZ) which is a typical characteristic of the FM order. Take into account of the classical results, we propose the three blue areas with different shadings in the global phase diagram (see Fig. \ref{fig:PhaseDiagram}) to be FM ordered phases (i.e., \emph{FM-A}, \emph{FM-B}, \emph{FM-C}) and they different from each other in the direction of the ordered moment which will be discussed in the next section. In Fig. \ref{fig:StructureFactors}(c)-(e), the SMSF peaked at the M-points indicating that the stripe ordered GS of the classical model persist in the quantum limit. It is worth to note that even the GS of the classical model near the AF Kitaev point was identified to be nematic ordered which is energetically degenerate with the stripe state, our ED results favor the idea that quantum flucations would select a stripe state. The four stripe phases designated as \emph{Stripe-A}, \emph{-B}, \emph{-C}, \emph{-D} in Fig. \ref{fig:PhaseDiagram}(a) different from each other only in the moment direction. Apart from these single-$\mathbf{Q}$ phases, we also identify a multi-$\mathbf{Q}$ phase, see the green area in Fig. \ref{fig:PhaseDiagram}(a). For $J$, $K$, $\Gamma$ in this area, the SMSF has high intensities at both the center and M-points of the first BZ and Fig. \ref{fig:StructureFactors}(f) is a typical SMSF profile of this phase. \textcolor{red}{$\cdots \cdots$}

\section{Moment Direction-Exact Diagonalization Results}
\textcolor{red}{Exact diagonalization results of the moment direction for FM and stripe phases. Left blank currently.}

\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig4.pdf}
    \caption{(Color online) Map of the probabilities.}
     \label{fig:Proabilities}
\end{figure}
